\documentclass[margin, centered]{res}
%\documentclass[11pt]{article}


\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
%\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = black,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}
\usepackage{makecell}
\usepackage{pbox}


\begin{document}

% Main Heading
\begin{center}
    \hspace{-\hoffset}
	\huge\bf{PROJECT PROPOSAL} \\

\end{center}

% Project Name
\begin{center}
    \hspace{-\hoffset}
	\huge\bf{Advanced Home Security System} \\
    
\end{center}

% Horizontal Line
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}


\begin{resume}

\section{Broad Subject Area} \textbf{Engineering Science}


\section{Specialization} \textbf{Mobile Computing}

\section{Title}  \textbf{Advanced Home Security System}

\section{Team Members}
			In alphabetical order:-
			
			\begin{table}[ht]
			\begin{tabular}{l c r}
			Debayan De & \(+91\) 8420 693 568 & debayan130@gmail.com\\
			Rohit Das & \(+91\) 8961 452 125  & rohit.das950@gmail.com\\
			Rudra Nil Basu & \(+91\) 8420 650 826 &  rudra.nil.basu.1996@gmail.com\\
			Sumitra Chowdhury & \(+91\) 8017 022 456  & chowdhury9995@gmail.com\\
			
			\end{tabular}
			\end{table}						
			
%			~\textbullet~ Debayan De\hspace{5mm} \hfill \(+91\) 8420 650 826 \hspace{5mm} \hfill rudra.nil.basu.1996@gmail.com\\
%			 ~\textbullet~ Rohit Das\hspace{5mm} \hfill \(+91\) 8961 452 125 \hspace{5mm} \hfill rohit.das950@gmail.com\\
%			~\textbullet~ Rudra Nil Basu\hspace{5mm} \hfill \(+91\) 8420 650 826 \hspace{5mm} \hfill rudra.nil.basu.1996@gmail.com\\
%			~\textbullet~ Sumitra Chowdhury\hspace{5mm} \hfill \(+91\) 8017 022 456 \hspace{5mm} \hfill chowdhury9995@gmail.com\\


\begin{center} 
\textbf{Project Details}\\
\end{center}

\section{Origin of Proposal}
%\begin{center} 
With the advent and advancement of technology, our primitive lives have changed fast. Our lifestyle has become more comfortable, thanks to the various arrays of gadgets and devices for communication, education, etc. But just like there are two sides of the same coin, technology has its shortcomings too. Crimes have existed in the past, and have only aggravated in nature. Now, with technology, criminals have found a new breath of life. So, technology and advanced gadgetry is our only weapon and protection against this misuse and abuse of scientific progress.\\
Our project is aimed at doing just that. Advanced Home Security and Armament System, or AHSAS in short, was planned keeping in mind the various problems people face because of the most common reasons for hiring and/or installing hi-tech security-home invasions. Breaking into homes keep claiming victims all the time. This system is all about trying to alleviate the situation and bring it under control. It is mainly aimed to work passively in case of an unauthorized intrusion. It is also created to protect any member trapped inside the house with the intruder. Live video footages will be taken, thus keeping track of the intruder. Even if someone manages to enter the house without setting off the alarm, door locks remotely operable by the home-owner can initiate lockdown, call the police and thus help law-enforcers to do their job.\\
The system will enable the user to remotely access the features, live footage and door-locking mechanisms along with the map of the house via an app on their mobile phones. It will also have an option of whether alerting the cops, firemen, paramedics or just call a close relative. People trapped inside the home during the intrusion can also call for help using a panic button present nearby in their current room.
%\end{center}
\section{Objectives}
\hspace{5mm} \\
~\textbullet~ To detect unnatural movements of intruders and set off an alarm.\\
~\textbullet~ Activating/Deactivating the security system via an android device.\\
~\textbullet~ Send live footages of intrusion and alert the home-owner/s via the android device\\
~\textbullet~ Control of the lights, doors and windows of the house via smartphone.\\
~\textbullet~ To alert cops, firemen, etc. in case of an emergency.\\
~\textbullet~ To maintain status quo of members trapped inside the home during the intrusion, if any.

\section{Methodology}
\hspace{5mm} \\
%~\textbullet~ Creating a detection system using \textbf{\textit{Matlab}}\\
~\textbullet~ Creating a detection system using motion sensors\\
~\textbullet~ Installing live-feed cameras for live footage of intrusion.\\
~\textbullet~ Installing proximity sensors and motion trackers to track movement of intruders.\\
~\textbullet~ Create a connection between an android device and the arduino board to control the various equipments of the house.


\section{Budget For Equipment}
\begin{table}[ht]
\caption{Budget for Equipment}
\begin{tabular}{|c |c |c |c |c|}
\hline \hline
Sl No & Name of the equipment & Quantity & Estimated cost(INR) & Justification\\
\hline

1 & Arduino Mega 2560 & 1 & 5500 & Controller\\ \hline
2 & \makecell{SainSmart LCD Module \\ For Arduino 20 X 4} & 1 & 660 & Display\\ \hline
3 & \makecell{Real Time Clock \\ DS1307 I2C AT24C32 Module} & 1 & 250 & ----------\\ \hline
4 & \makecell{Magnetic Door Window \\ Contact Reed Switch} & 4 & 588*4=2352 & \makecell{To detect opening \\of door/window} \\ \hline
5 & Breadboard & 1 & 800 & \makecell{Building the \\circuit}\\ \hline
6 & Breadboard jumper wires & 1 & 310 & \makecell{Building the \\circuit}\\ \hline
7 & \makecell{Matrix RGB \\LED Light} & 2 & 300*2=600 & \makecell{Danger\\signal}\\ \hline
%8 & Green LED & 3 & 200*3=600 & \makecell{Safe\\signal}\\ \hline
8 & 220 ohms resistor & 10 & 10*10=100 & \makecell{Circuit \\Resistance}\\ \hline
9 & Servo Motor & 4 & 600*4=2400 & \makecell{Moving Doors and \\Window of Room}\\ \hline
10 & Vivitar Recording camera & 2 & 5000*2=10000 & Record the events\\ \hline
11 & D-Link IP camera & 2 & 5000*2=10000 & \makecell{Real time \\broadcast of rooms}\\ \hline
12 & 10x 40-Pin Male Header 0.1" (2.54mm) & 10 & 1027 & Circuit Building \\ \hline
13 & \makecell{3 Colour RGB SMD \\LED Module 5050 full color} & 3 & 285*3=860 & \makecell{Display colors \\based on situation}\\ \hline
14 & \makecell{Adjust IR Pyroelectric Infrared \\IR PIR Motion Sensor} & 2 & 1600*2=3200 & \makecell{Motion Detection \\in the room}\\ \hline
15 & \makecell{Active Buzzer \\ Alarm Module Sensor Beep} & 1 & 1500 & To raise alarm\\ \hline
16 & \makecell{5V Four 4 Channel Relay Module \\With opt coupler} & 4 & 1080 & ---\\ \hline
%18 & \makecell{4 x 4 Matrix Array \\12 Key Membrane Switch Keypad} & 1 & 210 & ---\\ \hline
17 & 4.7k Potential meter & 1 & 1500 & Circuit Building\\ \hline
18 & 4.7k Multimeter & 1 & 1200 & Circuit Building\\ \hline
19 & ESP8266 wifi module & 1 & 250 & \makecell{Connect phone}\\ \hline
20 & Acrylic Boards and building materials & & 5706 & Building the structure\\ \hline
%19 & Form board & 1 & 360 & ---\\ 
%\hline
& \textbf{Total}   &   & 49895 & \\
\hline

\end{tabular}
\end{table}

\section{Plan of Work} The Plan of work is shown in the table below:

\begin{table}[ht]
\caption{Plan of Work}
\centering
\begin{tabular}{|c | c|}
\hline \hline
Work & Time \\
\hline
Survey and planning & First one week\\ \hline
Implementation & 6 weeks\\ \hline
Analysis & 1 week\\ \hline

\end{tabular}
\end{table}

\section{Place and Date} Kolkata\\
\today
\section{Signature}

\end{resume}



\end{document}